\newcommand{\lsd}[1] {\textit{#1}}
\section{Values relevants to initialize}
\begin{longtable}{||p{3cm}|p{10cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\end{longtable}

\section{Elements relevants to observe}
\begin{longtable}{||p{3cm}|p{10cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\end{longtable}

\section{List of all elements}
\subsection{Object \textbf{Root}}

Description: 
'Root' appears in the equation for: (Never Used).


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\end{longtable}

\subsection{Object \textbf{Market}}

Description: 'Market' appears in the equation for: (Never Used).


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{Init} &\textbf{Type: } Variable, 0 lags 
 
 
Initialize the model

'Init' appears in the equation for: (Never Used). \\ \hline 
\lsd{ProbFirmControl} &\textbf{Type: } Parameter
 
Probability of a firm to be controlled by the government. If found evading, it has to pay a fine on sales and a lump sum as penalty.

'ProbFirmControl' appears in the equation for: Evading.
 
 
 \textbf{Initial values:} 
 \\ \hline 
\lsd{ProbConsumerControl} &\textbf{Type: } Parameter
 
Probability for consumers to be controlled by the government. If found purchasing products from cheating firms they are subject to a fine, reducing their welfare.

'ProbConsumerControl' appears in the equation for: ProbAcceptEvasion, Shopping.
 
 
 \textbf{Initial values:} 
 \\ \hline 
\lsd{Shopping} &\textbf{Type: } Variable, 0 lags 
 
 
Round of purchase for each consumer. After purchasing, the government may control whether the supplier has evaded and punishes the consumer cutting setting the flag Fined=1

'Shopping' appears in the equation for: AvSales, Profit. \\ \hline 
\lsd{Statistics} &\textbf{Type: } Variable, 0 lags 
 
 
Stastics

'Statistics' appears in the equation for: (Never Used). \\ \hline 
\lsd{AvEvading} &\textbf{Type: } Parameter
 
'AvEvading' appears in the equation for: Statistics. \\ \hline 
\lsd{AvProfit} &\textbf{Type: } Parameter
 
'AvProfit' appears in the equation for: Statistics. \\ \hline 
\lsd{AvMemControlled} &\textbf{Type: } Parameter
 
'AvMemControlled' appears in the equation for: Statistics. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Demand}}

Description: 'Demand' appears in the equation for: (Never Used).


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{numConsumer} &\textbf{Type: } Parameter
 
'numConsumer' appears in the equation for: InitDemand. \\ \hline 
\lsd{numcLinks} &\textbf{Type: } Parameter
 
'numcLinks' appears in the equation for: InitDemand. \\ \hline 
\lsd{InitDemand} &\textbf{Type: } Variable, 0 lags 
 
 
Create a network of consumers connected randomly to each other.

Moreover, each consumer is endowed with a number of suppliers, choosing randomly, from which it will have to choose.

'InitDemand' appears in the equation for: Init. \\ \hline 
\lsd{numSuppliers} &\textbf{Type: } Parameter
 
'numSuppliers' appears in the equation for: InitDemand. \\ \hline 
\lsd{ExpPurchase} &\textbf{Type: } Parameter
 
'ExpPurchase' appears in the equation for: Purchase. \\ \hline 
\lsd{aUtility} &\textbf{Type: } Parameter
 
'aUtility' appears in the equation for: Purchase. \\ \hline 
\lsd{aProbEvasion} &\textbf{Type: } Parameter
 
'aProbEvasion' appears in the equation for: ProbAcceptEvasion. \\ \hline 
\lsd{WeightDirectExperience} &\textbf{Type: } Parameter
 
(no description available) \\ \hline 
\end{longtable}

\subsection{Object \textbf{Consumer}}

Description: 'Consumer' appears in the equation for: Shopping, InitDemand.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{idConsumer} &\textbf{Type: } Parameter
 
'idConsumer' appears in the equation for: InitDemand. \\ \hline 
\lsd{ProdUsed} &\textbf{Type: } Parameter
 
'ProdUsed' appears in the equation for: Purchase. \\ \hline 
\lsd{ConsumerWelfare} &\textbf{Type: } Parameter
 
'ConsumerWelfare' appears in the equation for: Purchase. \\ \hline 
\lsd{ProbAcceptEvasion} &\textbf{Type: } Variable, 1 lags 
 
 
Probability to include suppliers evading taxes within the option set for potential purchaes.

It is computed as a slow approximation to the average probability of evading from its own experience and that from other consumers.

'ProbAcceptEvasion' appears in the equation for: Purchase, ProbAcceptEvasion. \\ \hline 
\lsd{Fined} &\textbf{Type: } Parameter
 
'Fined' appears in the equation for: Shopping. \\ \hline 
\end{longtable}

\subsection{Object \textbf{cLink}}

Description: 'cLink' appears in the equation for: ProbAcceptEvasion, InitDemand.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{idcLink} &\textbf{Type: } Parameter
 
'idcLink' appears in the equation for: InitDemand. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Supplier}}

Description: 'Supplier' appears in the equation for: Purchase, InitDemand.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{idSupplier} &\textbf{Type: } Parameter
 
'idSupplier' appears in the equation for: InitDemand. \\ \hline 
\lsd{sapp} &\textbf{Type: } Parameter
 
'sapp' appears in the equation for: Purchase. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Supply}}

Description: 'Supply' appears in the equation for: (Never Used).


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{numfLinks} &\textbf{Type: } Parameter
 
'numfLinks' appears in the equation for: InitSupply. \\ \hline 
\lsd{numFirms} &\textbf{Type: } Parameter
 
'numFirms' appears in the equation for: InitSupply, InitDemand. \\ \hline 
\lsd{InitSupply} &\textbf{Type: } Variable, 0 lags 
 
 
Create a network of firms connected randomly to each other.

'InitSupply' appears in the equation for: Init. \\ \hline 
\lsd{Purchase} &\textbf{Type: } Function, 0 lags 
 

Choose one product and assign it to the consumer, pointed to by c->

The choice is probabilistic, depending on the acceptance of tax cheating firms by the consumer and on the Utility of the product offered by the sellers.

The equation also register the sale of the selected firm.

'Purchase' appears in the equation for: Shopping. \\ \hline 
\lsd{BasicUtility} &\textbf{Type: } Parameter
 
'BasicUtility' appears in the equation for: Utility. \\ \hline 
\lsd{UnitTax} &\textbf{Type: } Parameter
 
'UnitTax' appears in the equation for: Utility. \\ \hline 
\lsd{UnitGainEvasion} &\textbf{Type: } Parameter
 
'UnitGainEvasion' appears in the equation for: Utility, Evading, Profit. \\ \hline 
\lsd{UnitFine} &\textbf{Type: } Parameter
 
'UnitFine' appears in the equation for: Evading, Profit. \\ \hline 
\lsd{LumpPunishment} &\textbf{Type: } Parameter
 
'LumpPunishment' appears in the equation for: Evading, Profit. \\ \hline 
\lsd{aAvSales} &\textbf{Type: } Parameter
 
'aAvSales' appears in the equation for: AvSales, AvSalesEvading, AvSalesNoEvading. \\ \hline 
\lsd{UnitProfit} &\textbf{Type: } Parameter
 
'UnitProfit' appears in the equation for: Evading, Profit. \\ \hline 
\lsd{aMemControlled} &\textbf{Type: } Parameter
 
'aMemControlled' appears in the equation for: Evading. \\ \hline 
\lsd{weightPersonalMemory} &\textbf{Type: } Parameter
 
'weightPersonalMemory' appears in the equation for: Evading, AvSalesEvading, AvSalesNoEvading. \\ \hline 
\end{longtable}

\subsection{Object \textbf{Firm}}

Description: 'Firm' appears in the equation for: Shopping, Statistics, InitSupply.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{idFirm} &\textbf{Type: } Parameter
 
'idFirm' appears in the equation for: Purchase, InitSupply, InitDemand. \\ \hline 
\lsd{Sales} &\textbf{Type: } Parameter
 
'Sales' appears in the equation for: Purchase, AvSales, AvSalesEvading, AvSalesNoEvading, Profit, Shopping. \\ \hline 
\lsd{Evading} &\textbf{Type: } Variable, 0 lags 
 
 
Flag signaling whether the firm cheats on taxes (1) or pays (0)

In case of control it is set to 0.

Otherwise, it uses an estimation of the gain from paying taxes and not paying them, the discounted by the observed risk of being caught.

'Evading' appears in the equation for: Purchase, Utility, AvSalesEvading, AvSalesNoEvading, Profit, Shopping, Statistics, InitSupply. \\ \hline 
\lsd{Utility} &\textbf{Type: } Variable, 0 lags 
 
 
Utility for the consumer by choosing one product, mix of standard utility plus, in case of evasion, the difference of the unpaid tax and the extra gain for the producer.

'Utility' appears in the equation for: Purchase, InitSupply. \\ \hline 
\lsd{MemoryControlled} &\textbf{Type: } Parameter
 
'MemoryControlled' appears in the equation for: Evading, Statistics. \\ \hline 
\lsd{Punished} &\textbf{Type: } Parameter
 
'Punished' appears in the equation for: Evading, Profit. \\ \hline 
\lsd{AvSalesEvading} &\textbf{Type: } Variable, 1 lags 
 
 
Estimate of moving average of sales when evading

'AvSalesEvading' appears in the equation for: Evading, AvSalesEvading, InitSupply. \\ \hline 
\lsd{AvSalesNoEvading} &\textbf{Type: } Variable, 1 lags 
 
 
Estimate of moving sales when not evading

'AvSalesNoEvading' appears in the equation for: Evading, AvSalesNoEvading, InitSupply. \\ \hline 
\lsd{GainEvading} &\textbf{Type: } Parameter
 
'GainEvading' appears in the equation for: Evading. \\ \hline 
\lsd{CostEvading} &\textbf{Type: } Parameter
 
'CostEvading' appears in the equation for: Evading. \\ \hline 
\lsd{AvSales} &\textbf{Type: } Variable, 1 lags 
 
 
Compute the moving average of sales

'AvSales' appears in the equation for: Evading, AvSales, InitSupply. \\ \hline 
\lsd{Profit} &\textbf{Type: } Variable, 0 lags 
 
 
Profit are proportional to sale. If the firm evades taxes it also gains from a share of unpaid tax. In case of being caught it pays the fine.

The fine is computed on each single sale. Additionally, a lump punishment, such as a prison term, is added to the penalty.

'Profit' appears in the equation for: Statistics. \\ \hline 
\end{longtable}

\subsection{Object \textbf{fLink}}

Description: 'fLink' appears in the equation for: Evading, AvSalesEvading, AvSalesNoEvading, InitSupply.


\begin{longtable}{||p{3cm}|p{11cm}||}
  \hline
  \textbf{Label} & \textbf{Description} \\  \hline \endhead 
\lsd{idfLink} &\textbf{Type: } Parameter
 
'idfLink' appears in the equation for: InitSupply. \\ \hline 
\end{longtable}

